\textsf{Are large language models superhuman chemists?}

### 2024-10-31 src/tex/appendix.tex
fix changes
topic counts

            \multicolumn{1}{c}{\textbf{Analytical Chemistry} 166 Questions (5.8\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Chemical Preference} 1001 Questions (35\%)} \\

@@

            \multicolumn{1}{c}{\textbf{General Chemistry} 152 Questions (5.3\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} 94 Questions (3.3\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Materials Science} 89 Questions (3.1\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Organic Chemistry} 441 Questions (15.5\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Physical Chemistry} 179 Questions (6.3\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Technical Chemistry} 42 Questions (1.5\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Toxicity/Safety} 690 Questions (24.2\%)} \\

@@

            \multicolumn{1}{c}{\textbf{Knowledge} \variable{output/knowledge_count.txt} Questions} \\

@@

            \multicolumn{1}{c}{\textbf{Reasoning} \variable{output/reasoning_count.txt} Questions} \\

@@

            \multicolumn{1}{c}{\textbf{Intuition} \variable{output/intuition_count.txt} Questions} \\

@@

            \multicolumn{1}{c}{\textbf{Calculation} \variable{output/calculation_count.txt} Questions} \\

>>>>

            \multicolumn{1}{c}{\textbf{Analytical Chemistry} \variable{output/total_analytical.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Chemical Preference} \variable{output/total_chemical_preference.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{General Chemistry} \variable{output/total_general.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} \variable{output/total_inorganic.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Materials Science} \variable{output/total_materials_science.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Organic Chemistry} \variable{output/total_organic.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Physical Chemistry} \variable{output/total_physical.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Technical Chemistry} \variable{output/total_technical.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Toxicity/Safety} \variable{output/total_toxicity_safety.txt}} \\

@@

            \multicolumn{1}{c}{\textbf{Knowledge} \variable{output/knowledge_count.txt}\hspace{1.5em} Questions} \\

@@

            \multicolumn{1}{c}{\textbf{Reasoning} \variable{output/reasoning_count.txt}\hspace{1.5em} Questions} \\

@@

            \multicolumn{1}{c}{\textbf{Intuition} \variable{output/intuition_count.txt}\hspace{1.5em} Questions} \\

@@

            \multicolumn{1}{c}{\textbf{Calculation} \variable{output/calculation_count.txt}\hspace{1.5em} Questions} \\
